Geometry of Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees

### 2019-12-01 rnni_convexity.tex
new pseudocode csort

Note that the uniqueness of the $\rnni$ move in Line~\ref{alg:findpath:line:move_set_down} of Algorithm~\ref{alg:find_path} also implies that the algorithm is deterministic.
The running time of the algorithm is quadratic in the number of taxa.

@@

\begin{algorithm}[H]
\caption{$\csort$($T,R$)}
\label{alg:csort}
\begin{algorithmic}[1]
\STATE $T':= T$, $p := [T']$
\STATE $L_{T'}:=$ list representation of $T'$, $L_R:=$ list representation of $R$
\FOR {$i=1,\ldots,n-2$} \label{alg:csort:line:loop}
\STATE $j = 0$ \COMMENT{Special case: cherry}
\IF {$L_{T'}[0]$ is last element of $L_{T'}[0],L_{T'}[1],L_{T'}[2]$ in $L_R$}
\STATE Update $T'$: swap $L_{T'}[0]$ and $L_{T'}[2]$
\ELSIF {$L_{T'}[1]$ is last element of $L_{T'}[0],L_{T'}[1],L_{T'}[2]$ in $L_R$}
\STATE Update $\hat T$: swap $L_{T'}[1]$ and $L_{T'}[2]$
\ENDIF
\STATE $j = 2$
\WHILE {order of $L_{T'}[j]$ and $L_{T'}[j+1]$ different in $R$}
\STATE Update $T'$: Swap $L_{T'}[j]$ and $L_{T'}[j+1]$
\STATE $p = p+T', j = j + 1$
\ENDWHILE
\ENDFOR
\RETURN $p$
\end{algorithmic}
\end{algorithm}

>>>>

Note that the uniqueness of the $\rnni$ move in Line~\ref{alg:findpath:line:move_set_down} of the algorithm $\findpath$ also implies that the algorithm is deterministic.
The running time of the algorithm is quadratic in the number of taxa.

@@

\begin{algorithm}[H]
\caption{$\csort$($T,R$)}
\label{alg:csort}
\begin{algorithmic}[1]
\STATE $[x_1, x_2, \ldots, x_n] := R$, $T' := T$, $p = [T']$
\FOR {$i=n, \ldots, 3$}
    \FOR {$j=1, \ldots, i$}
        \IF {$T'[j] = x_i$}
            \STATE Update $T'$: swap $T'[j]$ and $T'[j+1]$
            \STATE $p = p + T'$
        \ENDIF
    \ENDFOR
\ENDFOR
\RETURN $p$
\end{algorithmic}
\end{algorithm}

% % Old version of algorithm csort that is closer to bubble sort
% \begin{algorithm}[H]
% \caption{$\csort$($T,R$)}
% \label{alg:csort}
% \begin{algorithmic}[1]
% \STATE $T':= T$, $p := [T']$
% \STATE $L_{T'}:=$ list representation of $T'$, $L_R:=$ list representation of $R$
% \FOR {$i=1,\ldots,n-2$} \label{alg:csort:line:loop}
% \STATE $j = 0$ \COMMENT{Special case: cherry}
% \IF {$L_{T'}[0]$ is last element of $L_{T'}[0],L_{T'}[1],L_{T'}[2]$ in $L_R$}
% \STATE Update $T'$: swap $L_{T'}[0]$ and $L_{T'}[2]$
% \ELSIF {$L_{T'}[1]$ is last element of $L_{T'}[0],L_{T'}[1],L_{T'}[2]$ in $L_R$}
% \STATE Update $\hat T$: swap $L_{T'}[1]$ and $L_{T'}[2]$
% \ENDIF
% \STATE $j = 2$
% \WHILE {order of $L_{T'}[j]$ and $L_{T'}[j+1]$ different in $R$}
% \STATE Update $T'$: Swap $L_{T'}[j]$ and $L_{T'}[j+1]$
% \STATE $p = p+T', j = j + 1$
% \ENDWHILE
% \ENDFOR
% \RETURN $p$
% \end{algorithmic}
% \end{algorithm}
